Output Summary

### 2021-08-03 03-post-process/output-plots.Rmd
Update all plots that display spawner-recruit and overwinter survival information
For multiple populations

@@

```{r eggs-to-parr, fig.width = 6, fig.height = 4}
# extract posterior samples of the BH productivity and capacity parameters
bh_params = post_subset(post, c("alpha", "^beta$"), matrix = T)
### LGR Smolt $\rightarrow O_0$ (NOR)

# extract posterior summaries of total spawners by brood year
Sa_tot = post_summ(post, "^Sa_tot[")
```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_nor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")
### LGR Smolt $\rightarrow O_0$ (HOR)

# extract posterior summaries of total parr recruits by brood year
Pb = post_summ(post, "^Pb[")
```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_hor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

# predict parr recruits along a sequence of spawner abundances
Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
f_pred = seq(0, max(f_tot[5,]), length = 30)
## Composition Data {.tabset .tabset-pills .tabset-fade}

Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
Pb_pred = post_summ(Pb_pred, "Pb_pred")
Within a single year, the values across all panels sum to one.

# fit ordinary least squares version
ols_fit = fit_fecund_BH(jags_data)$BH_fit
### Weir Sampling {.tabset .tabset-pills}

# draw 1000 random parameters
ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
#### CAT

# calculate predicted curve at each pair/summarize
ols_R_pred = t(sapply(1:1000, function(i) BH(f_pred, ols_params[i,1], ols_params[i,2])))
ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(1)
```

# graphical parameters
par(mar = c(3,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
#### LOS

# empty plot
plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
     xlab = "Total Egg Production (millions)", ylab = "Parr Recruits", xaxt = "n")
```{r lost-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(2)
```

x_ticks = axisTicks(par("usr")[1:2], log = F)
axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
#### MIN

# draw fitted relationship: Bayesian
polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(3)
```

# draw fitted relationship: OLS
polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
lines(ols_R_pred[2,] ~ f_pred, lty = 2)
lines(ols_R_pred[3,] ~ f_pred, lty = 2)
lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)
#### UGR

# draw state pairs + uncertainty
segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = "red")
segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = "red")
points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5))
```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(4)
```

## Total Eggs vs. Total Spawners
### Carcass Sampling {.tabset .tabset-pills}

This figure illustrates that total spawners is a reasonable index of total egg production. The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.
```{r carc-comp-fit-func}
carc_comp_fit_plot = function(j) {

```{r, fig.width = 6, fig.height = 4}
# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")
#### CAT

# extract posterior summaries of total spawners by brood year
Sa_tot = post_summ(post, "^Sa_tot[")
```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(1)
```

par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
plot(f_tot["mean",] ~ Sa_tot["mean",],
     ylim = c(0, max(f_tot["97.5%",])),
     xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
     ylab = "Total Egg Production (Millions)", xlab = "Total Spawners", las = 1, yaxt = "n")
y_ticks = axisTicks(par("usr")[3:4], log = F)
axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
#### LOS

segments(Sa_tot["2.5%",], f_tot["mean",], Sa_tot["97.5%",], f_tot["mean",], col = alpha("red", 0.5))
segments(Sa_tot["mean",], f_tot["2.5%",], Sa_tot["mean",], f_tot["97.5%",], col = alpha("red", 0.5))
points(f_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
abline(c(0, 1000), lty = 1)
abline(c(0, 1800), lty = 2)
abline(c(0, 3600), lty = 3)
legend("bottomright", title = "If Each Spawner Had:",
       legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
       lty = c(1,2,3), bty = "n")
```{r lost-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(2)
```

@@

This figure shows the inherent density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases. The horizontal line/region shows the theoretical maximum ($\alpha$) in the absence of density dependence.
#### MIN

```{r, fig.width = 6, fig.height = 4}
# extract posterior summaries of total egg production by brood year
f_tot = post_summ(post, "^f_tot[")
```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(3)
```

# extract posterior summaries of total parr recruits by brood year
Pb = post_summ(post, "^Pb[")
#### UGR

# conversion rates
Pb_per_f_tot = post_summ(post, "^Pb_per_f_tot[")
```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(4)
```

# max survival
alpha = post_summ(post, "^alpha")
## Spawn Status Data

par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
plot(Pb_per_f_tot["mean",] ~ f_tot["mean",],
     ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
     xlim = c(0, max(f_tot["97.5%",])), type = "n",
     ylab = "Parr per Egg", xlab = "Total Egg Production (Millions)", las = 1, xaxt = "n")
x_ticks = axisTicks(par("usr")[1:2], log = F)
axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
```{r spawn-status-fits, fig.width = 8, fig.height = 5}
par(oma = c(2,2,0,0))
layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))

segments(f_tot["2.5%",], Pb_per_f_tot["mean",], f_tot["97.5%",], Pb_per_f_tot["mean",], col = alpha("red", 0.5))
segments(f_tot["mean",], Pb_per_f_tot["2.5%",], f_tot["mean",], Pb_per_f_tot["97.5%",], col = alpha("red", 0.5))
points(Pb_per_f_tot["mean",] ~ f_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")

rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
abline(h = alpha["mean",], lwd = 2, col = "red")
box()
junk = sapply(1:jags_data$nj, plot_f)
```

@@

```{r, fig.width = 6, fig.height = 4}
# extract posterior summaries of total spawners by brood year
Sa_tot = post_summ(post, "^Sa_tot[")

# extract posterior summaries of total parr recruits by brood year
Pb = post_summ(post, "^Pb[")

# conversion rates
Pb_per_Sa_tot = post_summ(post, "^Pb_per_Sa_tot[")

par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
     ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
     xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
     ylab = "Parr per Spawner", xlab = "Spawners", las = 1)
segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
```

@@

```{r overwinter-survival, fig.width = 4, fig.height = 7}

# extract parr, scale it to PEU, and add to posterior samples
Pa = post_subset(post, "^Pa[", matrix = T)
Pa_scaled = Pa/jags_data$peu
colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
post = post_bind(post, Pa_scaled)

# summarize posterior of scaled parr
Pa_scaled_mean = array_format(post_summ(post, "Pa_scaled")["mean",])
Pa_scaled_lwr = array_format(post_summ(post, "Pa_scaled")["2.5%",])
Pa_scaled_upr = array_format(post_summ(post, "Pa_scaled")["97.5%",])

# create vectors to predict survival at: for credible regions and mean curve
Pa_scaled_seq = matrix(NA, 30, 2)
Pa_scaled_seq[,1] = seq(min(Pa_scaled_lwr[,1], na.rm = T), max(Pa_scaled_upr[,1], na.rm = T), length = 30)
Pa_scaled_seq[,2] = seq(min(Pa_scaled_lwr[,2], na.rm = T), max(Pa_scaled_upr[,2], na.rm = T), length = 30)

# extract posteriors of coefficients
gamma0 = post_subset(post, "gamma0", matrix = T)
gamma1 = post_subset(post, "gamma1", matrix = T)

# extract/format posterior summaries of realized survivals
phi_Pa_Mb_mean = array_format(post_summ(post, "^phi_Pa_Mb[")["mean",])
phi_Pa_Mb_lwr = array_format(post_summ(post, "^phi_Pa_Mb[")["2.5%",])
phi_Pa_Mb_upr = array_format(post_summ(post, "^phi_Pa_Mb[")["97.5%",])

# function to create predicted survival curves for one posterior sample
f = function(i) {
  pred_phi_Pa_Mb1 = plogis(gamma0[i,1] + gamma1[i,1] * Pa_scaled_seq[,1])
  pred_phi_Pa_Mb2 = plogis(gamma0[i,2] + gamma1[i,2] * Pa_scaled_seq[,2])

@@

# calculate predicted survivals and add to posterior samples
pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), f))
post = post_bind(post, pred_phi_Pa_Mb)

# summarize predicted survivals
pred_phi_Pa_Mb_mean = array_format(post_summ(post, "pred_phi_Pa_Mb")["mean",])
pred_phi_Pa_Mb_lwr = array_format(post_summ(post, "pred_phi_Pa_Mb")["2.5%",])
pred_phi_Pa_Mb_upr = array_format(post_summ(post, "pred_phi_Pa_Mb")["97.5%",])

# function to draw plot for one LH-type
plot_fun = function(i) {
  # blank plot of correct dimensions
  plot(1,1, type = "n", 
       ylim = range(pred_phi_Pa_Mb_lwr[,i], pred_phi_Pa_Mb_upr[,i], phi_Pa_Mb_lwr[,i], phi_Pa_Mb_upr[,i], na.rm = T),
       xlim = range(0, Pa_scaled_seq), 
       main = c("Fall Migrants", "Spring Migrants")[i]
  )

@@

  # realized survivals
  segments(Pa_scaled_lwr[,i], phi_Pa_Mb_mean[,i], Pa_scaled_upr[,i], phi_Pa_Mb_mean[,i], col = alpha("red", 0.5))
  segments(Pa_scaled_mean[,i], phi_Pa_Mb_lwr[,i], Pa_scaled_mean[,i], phi_Pa_Mb_upr[,i], col = alpha("red", 0.5))
  points(phi_Pa_Mb_mean[,i] ~ Pa_scaled_mean[,i], pch = 21, col = "red", bg = alpha("salmon", 0.5))
}

# create the plot
par(mfrow = c(2,1), mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1), oma = c(2,2,0,0))
plot_fun(1)
plot_fun(2)
mtext(side = 1, line = 1, outer = T, "LH-Specific Parr/PEU", cex = 1.2)
mtext(side = 2, line = 1, outer = T, "Overwinter Survival", cex = 1.2)
```

# Equivilency Rates

@@

```{r sar-plot, fig.width = 6, fig.height = 4}
# function to calculate posterior 
get_SAR_post = function(post, jags_data) {
  # extract posterior abundances
  Ra_post = post_subset(post, "^Ra[", T) # adults returning to Columbia River mouth
  Ma_post = post_subset(post, "^Ma[", T) # smolts at top of LGD

  # number of saved samples
  ni = post_dim(post, "saved")

  # first and last brood year SAR can be calculated for
  first_SAR_y = jags_data$kmax + 1
  last_SAR_y = jags_data$ny - jags_data$kmax

  # containers
  nat_SAR = hat_SAR = NULL

  # loop over mcmc iters
  for (i in 1:ni) {
    # extract quantities for this iter
    Ra = array_format(Ra_post[i,])
    Ma = array_format(Ma_post[i,])

>>>>

### LGR Smolt $\rightarrow O_0$ (NOR)

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_nor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

### LGR Smolt $\rightarrow O_0$ (HOR)

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_hor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

## Composition Data {.tabset .tabset-pills .tabset-fade}

Within a single year, the values across all panels sum to one.

### Weir Sampling {.tabset .tabset-pills}

#### CAT

```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(1)
```

#### LOS

```{r lost-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(2)
```

#### MIN

```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(3)
```

#### UGR

```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(4)
```

### Carcass Sampling {.tabset .tabset-pills}

```{r carc-comp-fit-func}
carc_comp_fit_plot = function(j) {

#### CAT

```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(1)
```

#### LOS

```{r lost-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(2)
```

#### MIN

```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(3)
```

#### UGR

```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(4)
```

## Spawn Status Data

```{r spawn-status-fits, fig.width = 8, fig.height = 5}
par(oma = c(2,2,0,0))
layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))

plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")

junk = sapply(1:jags_data$nj, plot_f)
```

@@

```{r eggs-to-parr, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior samples of the BH productivity and capacity parameters
  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)

  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))

  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))

  # extract posterior summaries of total parr recruits by brood year
  Pb = post_summ(post, sub_index("^Pb[.+,pop]", pop = j))

  # predict parr recruits along a sequence of spawner abundances
  Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
  f_pred = seq(0, max(f_tot[5,]), length = 30)

  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
  Pb_pred = post_summ(Pb_pred, "Pb_pred")

  # fit ordinary least squares version
  ols_fit = fit_fecund_BH(jags_data, pop = j)$BH_fit

  # draw 1000 random parameters
  ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))

  # calculate predicted curve at each pair/summarize
  ols_R_pred = t(sapply(1:1000, function(i) BH(f_pred, ols_params[i,1], ols_params[i,2])))
  ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])

  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)

  # draw fitted relationship: Bayesian
  polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
  lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)

  # draw fitted relationship: OLS
  polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
  lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
  lines(ols_R_pred[2,] ~ f_pred, lty = 2)
  lines(ols_R_pred[3,] ~ f_pred, lty = 2)
  lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)

  # draw state pairs + uncertainty
  segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = alpha("red", 0.5))
  segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = alpha("red", 0.5))
  points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
```

## Total Eggs vs. Total Spawners

This figure illustrates that total spawners is a reasonable index of total egg production. The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.

```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))

  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(f_tot["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(f_tot["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, yaxt = "n")

  # yaxis ticks
  y_ticks = axisTicks(par("usr")[3:4], log = F)
  axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)

  segments(Sa_tot["2.5%",], f_tot["mean",], Sa_tot["97.5%",], f_tot["mean",], col = alpha("red", 0.5))
  segments(Sa_tot["mean",], f_tot["2.5%",], Sa_tot["mean",], f_tot["97.5%",], col = alpha("red", 0.5))
  points(f_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
  abline(c(0, 1000), lty = 1)
  abline(c(0, 1800), lty = 2)
  abline(c(0, 3600), lty = 3)

  if (j == 1) {
    legend("bottomright", title = "If Each Spawner Had:",
           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
           lty = c(1,2,3), bty = "n", cex = 0.75)
  }
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
```

@@

This figure shows the inherent density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases. The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.

```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))

  # conversion rates
  Pb_per_f_tot = post_summ(post, sub_index("^Pb_per_f_tot[.+,pop]", pop = j))

  # max survival
  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(Pb_per_f_tot["mean",] ~ f_tot["mean",],
       # ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
       ylim = c(0, 1),
       xlim = c(0, max(f_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])

  # x-axis
  x_ticks = axisTicks(par("usr")[1:2], log = F)
  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)

  segments(f_tot["2.5%",], Pb_per_f_tot["mean",], f_tot["97.5%",], Pb_per_f_tot["mean",], col = alpha("red", 0.5))
  segments(f_tot["mean",], Pb_per_f_tot["2.5%",], f_tot["mean",], Pb_per_f_tot["97.5%",], col = alpha("red", 0.5))
  points(Pb_per_f_tot["mean",] ~ f_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
  abline(h = alpha["mean",], lwd = 2, col = "red")
  box()
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
mtext(side = 1, outer = T, line = 0.25, "Parr per Egg")
```

@@

```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))

  # conversion rates
  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[.+,pop]", pop = j))

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1)

  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
mtext(side = 1, outer = T, line = 0.25, "Parr per Spawner")
```

@@

```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
plot_fn = function(j) {
  # extract parr, scale it to PEU, and create new post object
  Pa = post_subset(post, sub_index("^Pa[.+,.,pop]", pop = j), matrix = TRUE)
  Pa_scaled = Pa/jags_data$peu[j]
  colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
  post_pa = post_convert(cbind(postpack:::id_mat(post), Pa_scaled))

  # summarize posterior of scaled parr
  Pa_scaled_mean = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["mean",])
  Pa_scaled_lwr = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["2.5%",])
  Pa_scaled_upr = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["97.5%",])

  # create vectors to predict survival at: for credible regions and mean curve
  Pa_scaled_seq = matrix(NA, 30, 2)
  Pa_scaled_seq[,i_fall] = seq(min(Pa_scaled_lwr[,i_fall,j], na.rm = TRUE), max(Pa_scaled_upr[,i_fall,j], na.rm = T), length = 30)
  Pa_scaled_seq[,i_spring] = seq(min(Pa_scaled_lwr[,i_spring,j], na.rm = TRUE), max(Pa_scaled_upr[,i_spring,j], na.rm = T), length = 30)

  # extract posteriors of coefficients
  gamma0 = post_subset(post, sub_index("gamma0[.,pop]", pop = j), matrix = TRUE)
  gamma1 = post_subset(post, sub_index("gamma1[.,pop]", pop = j), matrix = TRUE)

  # extract/format posterior summaries of realized survivals
  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["mean",])
  phi_Pa_Mb_lwr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["2.5%",])
  phi_Pa_Mb_upr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["97.5%",])

  # function to create predicted survival curves for one posterior sample
  pred_fn = function(i) {
    pred_phi_Pa_Mb1 = plogis(gamma0[i,1] + gamma1[i,1] * Pa_scaled_seq[,1])
    pred_phi_Pa_Mb2 = plogis(gamma0[i,2] + gamma1[i,2] * Pa_scaled_seq[,2])

@@

  # calculate predicted survivals and add to posterior samples
  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
  post_pa = post_bind(post_pa, pred_phi_Pa_Mb)

  # summarize predicted survivals
  pred_phi_Pa_Mb_mean = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["mean",])
  pred_phi_Pa_Mb_lwr = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["2.5%",])
  pred_phi_Pa_Mb_upr = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["97.5%",])

  # function to draw plot for one LH-type
  plot_fn2 = function(i) {
    # blank plot of correct dimensions
    plot(1,1, type = "n", 
         ylim = range(pred_phi_Pa_Mb_lwr[,i], pred_phi_Pa_Mb_upr[,i], phi_Pa_Mb_lwr[,i,j], phi_Pa_Mb_upr[,i,j], na.rm = T),
         xlim = range(0, Pa_scaled_seq), 
         main = ifelse(i == 1, pops[j], "")
    )

@@

    # realized survivals
    segments(Pa_scaled_lwr[,i,j], phi_Pa_Mb_mean[,i,j], Pa_scaled_upr[,i,j], phi_Pa_Mb_mean[,i,j], col = alpha("red", 0.5))
    segments(Pa_scaled_mean[,i,j], phi_Pa_Mb_lwr[,i,j], Pa_scaled_mean[,i,j], phi_Pa_Mb_upr[,i,j], col = alpha("red", 0.5))
    points(phi_Pa_Mb_mean[,i,j] ~ Pa_scaled_mean[,i,j], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
  }

  # create the plot
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot_fn2(1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
  plot_fn2(2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")

}

par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, line = 1.5, outer = T, "LH-Specific Parr/PEU", cex = 1.2)
mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
```

# Equivilency Rates {.tabset .tabset-pills}

@@

```{r adults-per-smolt, fig.width = 6, fig.height = 5}
sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]

plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = c(6:29), LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

  # summarize rates
  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[.+,origin,pop]", origin = o_nor, pop = j)) * 100
  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[.+,origin,pop]", origin = o_hor, pop = j)) * 100
